### 2021-03-12 paper_1.tex
End seriously paper1

\subsubsection{Low-Level Feature Extraction}
In the selective path, features such as complementary colors ($ f_{rg} = r-g$, 
$ f_{by} = b-(r+g)/2 $), luminance ($ f_{lum} = (r+g+b)/3 $) and texture are 
extracted. In addition, the density of the edges ($ f_{ed} $) is extracted, useful to 
represent the level of density of the edges, smoothed by a median filter of 
11x11 pixels.

\subsubsection{Bayesian Inference With Contour Guidance}
Bayesian inference gives the possibility to calculate the probability that a 
pixel \emph{x} may belong to a salient structure \emph{s}. This probability is computed as:
$$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
finally $ p(s)=Sw $ represents the CBSP value. The implementation 
details are as follows.
\begin{enumerate}
    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization 
    of the map obtained from $ p(s) $, separates the salient structures 
    from the background, all through the use of a threshold. This 
    threshold is calculated using local parameters (color, luminance, etc.), 
    a threshold $ T_k $ no greater than 50\% of the size of the entire image, useful 
    for denoting the size of the salient structure, an initial non-zero 
    weight and finally two sets of pixels ($ B_{T_k}$ , $ S_{T_k}$) corresponding to the background 
    and foreground (salient structure).
    \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
    when the difference between the average pixel values of its 
    salient structure and those of the background is large enough, i.e. when $ w_i $ 
    takes on a satisfiable value.
    \item \emph{Calculate the Observation Likelihood}:in order to calculate the observed 
    probabilities, the different color channels \emph{($ f_{lum}, f_{rg}, f_{by}, f_{ed} $)} are used, 
    and the distribution functions $ p(x_i | S_{T_{opt}}) $ and $ p(x_i | B_{T_{opt}}) $ where $ S_{T_{opt}} $ 
    represents the set of pixels belonging to the structure salient, while 
    $ B_{T_{opt}} $ represents the set of pixels belonging to the background.
    $$ p(x|s) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | S_{T_{opt}}))^{w_i}} $$
    $$ p(x|b) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | B_{T_{opt}}))^{w_i}} $$
    \item \emph{Enhance the Salient Structure by Iterating}: the salient structures, at 
    each instant \emph{t}, with $ t = t_0,…, t_n $, are iteratively improved by applying 
    a median filter on each of them. In addition, the weight attributed to 
    the importance of each feature is changed. Finally, the CGVS model 
    will operate on a set of instants \emph{t}, thus forming the contour-guided 
    visual search.
\end{enumerate}

>>>>

\subsubsection{Low-Level Feature Extraction}
In the selective path, features such as complementary colors ($ f_{rg}, f_{by}$), luminance 
($ f_{lum} $) and texture are extracted. In addition, the density of the 
edges ($ f_{ed} $) is extracted, useful to represent the level of density of the edges, 
smoothed by a median filter of 11x11 pixels.
$$ f_{rg} = r-g $$
$$ f_{by} = b-(r+g)/2 $$
$$ f_{lum} = (r+g+b)/3 $$

\subsubsection{Bayesian Inference With Contour Guidance}
Bayesian inference gives the possibility to calculate the probability that a 
pixel \emph{x} may belong to a salient structure \emph{s}. This probability is computed as:
$$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
finally $ p(s)=Sw $ represents the CBSP value. The implementation 
details are as follows.
\begin{enumerate}
    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization 
    of the map obtained from $ p(s) $, separates the salient structures 
    from the background, all through the use of a threshold. This 
    threshold is calculated using local parameters (color, luminance, etc.), 
    a threshold $ T_k $ no greater than 50\% of the size of the entire image, useful 
    for denoting the size of the salient structure, an initial non-zero 
    weight and finally two sets of pixels ($ B_{T_k}$ , $ S_{T_k}$) corresponding to the background 
    and foreground (salient structure).
    $$ T_{opt} = \argmax\limits_{T_k} \sqrt{\sum_{i} (\omega_i^0*(\tilde{S}^i_{T_{k}}) - (\tilde{B}^i_{T_{k}}))^2} $$
    \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
    when the difference between the average pixel values of its 
    salient structure and those of the background is large enough, i.e. when $ \omega_i $ 
    takes on a satisfiable value.
    $$ \omega_i = \frac{1}{\mu} * | \tilde{S}^i_{T_{opt}} - \tilde{B}^i_{B_{opt}} |$$
    \item \emph{Calculate the Observation Likelihood}:in order to calculate the observed 
    probabilities, the different color channels \emph{($ f_{lum}, f_{rg}, f_{by}, f_{ed} $)} are used, 
    and the distribution functions $ p(x_i | S_{T_{opt}}) $ and $ p(x_i | B_{T_{opt}}) $ where $ S_{T_{opt}} $ 
    represents the set of pixels belonging to the structure salient, while 
    $ B_{T_{opt}} $ represents the set of pixels belonging to the background.
    $$ p(x|s) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | S_{T_{opt}}))^{w_i}} $$
    $$ p(x|b) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | B_{T_{opt}}))^{w_i}} $$
    \item \emph{Enhance the Salient Structure by Iterating}: the salient structures, at 
    each instant \emph{t}, with $ t = t_0,…, t_n $, are iteratively improved by applying 
    a median filter on each of them. In addition, the weight attributed to 
    the importance of each feature is changed. Finally, the CGVS model 
    will operate on a set of instants \emph{t}, thus forming the contour-guided 
    visual search.
\end{enumerate}
